%=== FRONT PART ===
%=== ACKNOWLEDGEMENT ===
\fancypagestyle{addin}{
\fancyhead[R]{\bf \textsl{ACKNOWLEDGEMENTS} \vspace{0.1in}}
}
%\begin{center}
\chapter*{\centering Acknowledgements}
\begin{spacing}{1.4}
\setlength{\parskip}{0.3in}
\thispagestyle{addin}
%\end{center}
\addcontentsline{toc}{chapter}{Acknowledgement}

First of all, I would express my deepest gratitude to three supervisors of my dissertation: Associate Professor Soong Boon Hee, Associate Professor Teoh Eam Khwang and Dr Wang Jianggang. Assoc. Prof. Teoh has retired from the school, but he continued to help me do research, always remember me in Chinese festivals, and give me great encouragement. Much appreciate your kindness and patience, which is precious for a new student in Singapore! Assoc. Prof. Soong has been guiding me all the way and helped me a lot in my PhD application, offering me precious guidance and insightful suggestions. Thank you very much!

Second, I would also express great thanks and respects to my excellent team, the leader Mr Prabhu Shankar Mahendran, a year four PhD candidate, and Mr Tan Kai Liang, a year four undergraduate student. Mr Prabhu is wise and patient, always showing gentle and kindness, and continuously inspiring the team to progress, always leading us to work in the right direction. He provided lots of valuable suggestion on my PhD application. I hope to become a person like him in my PhD years. Mr Tan is very reliable and trustworthy. Our team makes much progress with his outstanding efforts. Appreciate much for meeting you.

Third, I would thank Lanning Zeng, Ariana Pei, Jeff Lo, Xiaopu Zhang, and my pastor, Associate Professor Che Ming Yau. Thanks to my parents and those who have been supporting me. Thank you for encouraging me when I am stressed out, and for all the unforgettable memories with each of you. Nice to meet you.

Thank you and best regards,\\
Tian Zichen, April 2021

\end{spacing}
\newpage
%=== END OF ACKNOWLEDGEMENT  ===